Decentralised Authoring, Annotations and Notifications for a Read-Write Web with dokieli

### 2017-04-07 index.tex
consistent typography

\par dokieli is \textit{self-replicating}, in that the reader of a dokieli document can spawn an instance — either a copy or a brand new empty document — into their own storage space at the click of a button.

>>>>

\par dokieli is \textit{self-replicating}, in that the reader of a dokieli document can spawn an instance—either a copy or a brand new empty document—into their own storage space at the click of a button.
